A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-08-20 paper.Rmd

- Explain formats like XML, as people might come into formats that wany XML.
- The power lies in the contrast to a csv codebook, as there is a defined, nested structure.
- Ontologies and domain specific metadata standards such as EML might also be worth mentioning.
- introduce the holy grail of the semantic web: JSON-LD
- readers just been advised to make a:
  - a csv codebook,
  - put that in the README
  - then make a JSON file. 
Is there a way to discuss strategies on harmonising all these formats?

>>>>

- Explain formats like XML, as people might come into formats that wany XML.
- The power lies in the contrast to a csv codebook, as there is a defined, nested structure.
- Ontologies and domain specific metadata standards such as EML might also be worth mentioning.
- introduce the holy grail of the semantic web: JSON-LD

- readers just been advised to make a:
  - a csv codebook,
  - put that in the README
  - then make a JSON file. 
Is there a way to discuss strategies on harmonising all these formats?

- we could map out how these things link together (e.g., you can turn JSON into xml with package ...)
- make a table that describes how to do something in R, or Python, or Julia
-
